---
Import data for the developmental plasticity examination. File name is "dp.csv"
```{r}
dp = read.table(file.choose(),  na.strings =".", header=T, sep=",")
```

Import data for the alaysis of the Morris Water Maze data. File name is "mwm.csv"

```{r}
mwm = read.table(file.choose(),  na.strings =".", header=T, sep=",")
```

Import data for the analysis of the linear maze. File name is "linearmaze.csv"
```{r}
linear = read.table(file.choose(),  na.strings =".", header=T, sep=",")
```

Load the necessary libraries
```{r}
library(lme4)
library(lmerTest)
library(ggplot2)
library(plyr)
```

MANOVA looking at the developmental pattern and the individual ANOVAs for all individuals in both experiments
```{r}
developMANOVA <- manova(cbind(DevRate, Gweight, Gsize)~Treatment, data=dp)
summary(developMANOVA)
summary.aov(developMANOVA)
```

MWM analysis
------------

Centering and Subseting data 
```{r}
mwm$DevRateCent <- scale(mwm$DevRate, center = TRUE, scale = TRUE)
mwm$GweightCent <- scale(mwm$Gweight, center = TRUE, scale = TRUE)
mwm$WeightAfterCent <- scale(mwm$WeightAfter, center = TRUE, scale = TRUE)

mwm$StartPosition <- factor(mwm$StartPosition)

##To examine the first trial on it's own
mwmTrial1 <- subset(mwm, Trial=="1")

##To remove trial 1, MT, and D2 from the trials
mwmTrials<-mwm[-which(mwm$Trial == "MT"), ]
mwmTrials<-mwmTrials[-which(mwmTrials$Trial == "D2"), ]
mwmTrials<-mwmTrials[-which(mwmTrials$Trial == "1"), ]

##To examine the D2 trial on it's own
mwmTrialD2 <- subset(mwm, Trial=="D2")

##To examine the MT trial on it's own
mwmTrialMT <- subset(mwm, Trial=="MT")

##To examine only the trials where individuals were successful
mwmTrialSucc <- subset(mwm, Complete=="Yes")
```



Do any factors predict success rates
```{r}
SuccessRate <- lm(Successes ~ Treatment + DevRateCent + WeightAfterCent, data = mwmTrial1)
summary(SuccessRate)


ggplot(mwmTrial1, aes(x = DevRate, y = Successes)) + 
  geom_point(size = 4, position = position_dodge(width = 0.0005)) + 
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("Development Rate") +
  ylab("The Number of Successful Trials") +
  theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y=element_text(vjust=0.25),
        axis.title.x=element_text(vjust=0.25),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()
        )         
        
        
```

Of the successful individuals, is there anything that predicts their performance?
```{r}
CompTime <- lmer(Time_0 ~ Treatment + DevRate + WeightAfter + (1 | Cricket), data = mwmTrialSucc)
summary(CompTime)
```


How treatment, development rate, trial number, the starting position of the cricket affect the time to completion. 

```{r}
##Here it is with a max of 300 seconds, which assumes completion
Success <- lmer(Time_300 ~ Treatment + DevRate + WeightAfter + Trial + StartPosition + DevRate*Trial + (1 | Cricket), data = mwmTrials)
anova(Success)
summary(Success)


ggplot(mwmTrials, aes(x=Trial, y=Time_300)) + geom_violin() + guides(fill=FALSE) +
  ylab("Time to Completion") +
  xlab("Trial Number") + theme_bw() +
  theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y=element_text(vjust=0.65),
        axis.title.x=element_text(vjust=0.25),
        axis.text=element_text(size=18),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) 



```



Linear Maze analysis
--------------------

Subseting data 
```{r}
linear$DevRateScale <- scale(linear$DevRate, center = TRUE, scale = TRUE)
linear$GweightScale <- scale(linear$Gweight, center = TRUE, scale = TRUE)
linear$WeightAfterScale <- scale(linear$WeightAfter, center = TRUE, scale = TRUE)

linear$logTE_ALL <- log(linear$TE_ALL+1)
linear$logT_tcP <- log(linear$T_tcP+1)
linear$logT_tcS <- log(linear$T_tcS+1)

linear$Complete <- factor(linear$Complete)


##To separate Day 1 and Day 2
lmDay1 <- subset(linear, Day=="1")
lmDay2 <- subset(linear, Day=="2")

##To separate Just Day 1 Trial 1
lmTrial1 <- subset(lmDay1, Trial=="1")


##To separate the MT from the rest of the trials
lmDay1Trials <-lmDay1[-which(lmDay1$Trial == "MT"), ]
lmDay1Trials <-lmDay1Trials[-which(lmDay1$Trial == "1"), ]

##Just successful ones
lmDay1TrialsComp <- subset(lmDay1Trials, Complete=="1")

##Just the mirror trial
lmDay1MT <-subset(lmDay1, Trial=="MT")


```

Do treatments differ by how many trials females complete on average

```{r}
ddply(lmTrial1, c("Treatment"), summarise,
                     N = length(NumTrials),
                     mean = mean(NumTrials),
                     sd = sd(NumTrials),
                     se = sd/sqrt(N))


Complete <- glmer(Complete ~ DevRateScale + WeightAfterScale + Treatment + Trial + (1|Cricket), family=binomial, data=lmDay1Trials)
anova(Complete)
summary(Complete)


TimeComplete <- lmer(TOTAL.T ~ Treatment + Trial + DevRateScale + WeightAfterScale + (1|Cricket), data = lmDay1TrialsComp)
anova(TimeComplete)
summary(TimeComplete)


Errors <- lmer(logTE_ALL ~ DevRateScale + WeightAfterScale + Treatment + Trial + (1|Cricket), data=lmDay1Trials)
anova(Errors)
summary(Errors)

Pauses <- lmer(logT_tcP ~ DevRateScale + WeightAfterScale + Treatment + Trial + (1|Cricket), data=lmDay1Trials)
anova(Pauses)
summary(Pauses)

Shoves <- lmer(logT_tcS ~ DevRateScale + WeightAfterScale + Treatment + Trial + (1|Cricket), data=lmDay1Trials)
summary(Shoves)
anova(Shoves)

ddply(lmDay1Trials, c("Treatment"), summarise,
                     N = length(logT_tcP),
                     mean = mean(logT_tcP),
                     sd = sd(logT_tcP),
                     se = sd/sqrt(N))

ggplot(lmDay1Trials, aes(x=Treatment, y=T_tcP)) + geom_violin() + 
  guides(fill=FALSE) + theme_bw() +
  xlab("Treatment") +
  ylab("The Number of Pauses") +
  theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y=element_text(vjust=0.65),
        axis.title.x=element_text(vjust=0.25),
        axis.text=element_text(size=18),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()
        )
        
ggplot(lmDay1TrialsComp, aes(x=Treatment, y=TOTAL.T)) + geom_violin() + guides(fill=FALSE) +
  ylab("Time to Completion") +
  xlab("Trial Number") + theme_bw() +
  theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y=element_text(vjust=0.65),
        axis.title.x=element_text(vjust=0.25),
        axis.text=element_text(size=18),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) 


CompleteMT <- glm(Complete ~ DevRateScale + WeightAfterScale + Treatment, family=binomial, data=lmDay1MT)
summary(CompleteMT)


TimeCompleteMT <- lm(TOTAL.T ~ Treatment + DevRateScale + WeightAfterScale, data = lmDay1MT)
anova(TimeCompleteMT)
summary(TimeCompleteMT)

Day2 <- glm(Complete ~ DevRateScale + WeightAfterScale + Treatment, family=binomial, data=lmDay2)
summary(Day2)

TimeCompleteDay2 <- lm(TOTAL.T ~ Treatment + DevRateScale + WeightAfterScale, data = lmDay2)
anova(TimeCompleteDay2)

```



